Reaction-diffusion spatial modeling of COVID-19 in Chicago

### 2021-12-20 version3/version3.tex
spatial model update

>>>>

	Even if the model is based on faulty assumptions, we would still expect to see some evidence of diffusion in the spatial simulations.
	Examining the simulated populations of $S$ and $A$ (Figure \ref{fig:app-pops}), we immediately see there is a problem with the spatial simulation.
	The bounds on the computation domain are clearly not sufficient to describe the boundaries of the city, since the $S$ and $A$ populations almost entirely diffuse into Lake Michigan.
	As a result, there are very few int
